Validity of a model for a cantilever two-dimensional beam

### 2024-04-07 files/Chapter4/Validity_Timo.tex
Section capital

\subsection{The models}
The cantilever Timoshenko beam model is defined in section \ref{ssec:1D_Model:ModelProblems}, and is referred to as Problem T-2. The cantilever two-dimensional beam model is defined in section \ref{ssec:2D_Model:ModelProblem}, and is referred to as Problem 2D-1.

@@

In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
introduced. The paramater is given here again for convenience:
\begin{eqnarray*}
	\alpha = \frac{A\ell^2}{I}.
\end{eqnarray*}

@@

\subsection{Calculating the eigenvalues and eigenvectors}
In section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided. And in section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.

For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method. In section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived. Specifically, section \ref{2dFEM_EP} derives the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.

\subsubsection{Problem 2D-1E}
Find a real number $\lambda$ and a vector $\bar{u} \in R^n$ such that
\begin{eqnarray}
	K\bar{u} & = & M\lambda{\bar{u}},
\end{eqnarray} where $M$ and $K$ are the standard Finite Element Method matrices defined in section \ref{sec:FEM:2D}.

>>>>

\subsection{The models}
The cantilever Timoshenko beam model is defined in Section \ref{ssec:1D_Model:ModelProblems}, and is referred to as Problem T-2. The cantilever two-dimensional beam model is defined in Section \ref{ssec:2D_Model:ModelProblem}, and is referred to as Problem 2D-1.

@@

In the derivation of the Timoshenko beam model in Section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
introduced. The paramater is given here again for convenience:
\begin{eqnarray*}
	\alpha = \frac{A\ell^2}{I}.
\end{eqnarray*}

@@

\subsection{Calculating the eigenvalues and eigenvectors}
In Section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided. And in Section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.

For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method. In Section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived. Specifically, Section \ref{2dFEM_EP} derives the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.

\subsubsection{Problem 2D-1E}
Find a real number $\lambda$ and a vector $\bar{u} \in R^n$ such that
\begin{eqnarray}
	K\bar{u} & = & M\lambda{\bar{u}},
\end{eqnarray} where $M$ and $K$ are the standard Finite Element Method matrices defined in Section \ref{sec:FEM:2D}.

### 2024-04-07 files/Chapter5/2D_FEM.tex
Section capital

The outline of the chapter is as follows.
\begin{itemize}
	\item[] Section \ref{sec:FEM:2D} FEM for a cantilever two-dimensional elastic body. This is problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
	\item[] Section \ref{sec:FEM:3D} FEM for a cantilever three-dimensional elastic body. This is problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.
	\item[] Section \ref{sec:FEM:Plate} FEM for a cantilever Reissner-Mindlin plate. This is problem P-1 in section \ref{ssec:P_Model:ModelProblems}.
\end{itemize}

@@

\subsubsection{Cantilever elastic body}
Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
\FloatBarrier
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

@@

In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2D-1V. Some of the results from section \ref{sec:2D_Model} are repeated here for convenience. Using the reference configuration, these results are rewritten from a general form to a model specific form.

>>>>

The outline of the chapter is as follows.
\begin{itemize}
	\item[] Section \ref{sec:FEM:2D} FEM for a cantilever two-dimensional elastic body. This is problem 2D-1 in Section \ref{ssec:2D_Model:ModelProblem}.
	\item[] Section \ref{sec:FEM:3D} FEM for a cantilever three-dimensional elastic body. This is problem 3D-1 in Section \ref{ssec:3D_Model:ModelProblems}.
	\item[] Section \ref{sec:FEM:Plate} FEM for a cantilever Reissner-Mindlin plate. This is problem P-1 in Section \ref{ssec:P_Model:ModelProblems}.
\end{itemize}

@@

\subsubsection{Cantilever elastic body}
Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D-1 in Section \ref{ssec:2D_Model:ModelProblem}.
\FloatBarrier
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

@@

In Section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2D-1V. Some of the results from Section \ref{sec:2D_Model} are repeated here for convenience. Using the reference configuration, these results are rewritten from a general form to a model specific form.

### 2024-04-07 files/Chapter5/3D_FEM.tex
Section capital

Using this notation, the boundary conditions are similar to the two-dimensional model in section \ref{sssec:2D_Model:RefConf}, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.

\subsubsection{Cantilever elastic body}
Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma$ and free-hanging at all the other sides. This is Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.
\FloatBarrier
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

@@

In section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3D-1V. This general form can now be rewritten as in a model specific form using the reference configuration. For convenience, some of the results from section \ref{sec:3D_Model} are repeated here.

@@

\subsection{Galerkin approximation}
As mentioned in the previous section, section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised. For this three-dimensional body, three-dimensional elements shapes are required. The elements used in this dissertation are rectangular prismatic elements. These elements are also known as `brick-shaped' elements and is described in \cite{Wu06}. This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.

@@

For this three-dimensional model, piecewise Hermite tri-cubic basis functions are used. Although this is more complex than using piecwise tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.

>>>>

Using this notation, the boundary conditions are similar to the two-dimensional model in Section \ref{sssec:2D_Model:RefConf}, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.

\subsubsection{Cantilever elastic body}
Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma$ and free-hanging at all the other sides. This is Problem 3D-1 in Section \ref{ssec:3D_Model:ModelProblems}.
\FloatBarrier
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

@@

In Section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3D-1V. This general form can now be rewritten as in a model specific form using the reference configuration. For convenience, some of the results from Section \ref{sec:3D_Model} are repeated here.

@@

\subsection{Galerkin approximation}
As mentioned in the previous section, Section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised. For this three-dimensional body, three-dimensional elements shapes are required. The elements used in this dissertation are rectangular prismatic elements. These elements are also known as `brick-shaped' elements and is described in \cite{Wu06}. This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.

@@

For this three-dimensional model, piecewise Hermite tri-cubic basis functions are used. Although this is more complex than using piecwise tri-linear basis functions, as mentioned in Section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.

### 2024-04-07 files/Chapter5/PlateModel.tex
Chapter 3
Section capital

\subsubsection{Reference configuration for a rectangular plate}
Let $\left\{e_1,e_2\right\}$ be a right-handed orthonormal basis for $R^2$. Although this basis seems identical to the two-dimensional beam in section \ref{sssec:2D_Model:RefConf}, it is fact different. It would be more appropriate to use $e_1$ and $e_3$ for this plate model. However the use of $e_1$ and $e_2$ is kept to reiterate that this is in fact a two-dimensional model.

@@

\subsubsection{Cantilever plate model}
Consider a rectangular Reissner-Mindlin plate clamped rigidly to a surface at $\Sigma$ and free hanging on the remaining edges. This plate model is presented in section \ref{ssec:P_Model:ModelProblems} as Problem P-1.

@@

In section \ref{ssec:P_Model:ModelProblems} the variational problem for the cantilever Reissner-Mindlin plate is defined by Problem P-1V. For convenience, the relevant results from section \ref{ssec:P_Model:ModelProblems} are repeated.

@@

\subsection{Galerkin approximation}
To discretise the body $\Omega$, the same shapes as in section \ref{ssec:2D_Model:Galerkin} are used.

@@

These basis functions are bi-cubic basis functions.

@@

\subsection{System of ordinary differential equations}\label{plate_fem_g}
The standard FEM matrices $K_{11}$, $K_{12}$, $K_{21}$, $K_{22}$ and $M_F$ where presented in section \ref{ssec:2DFEM:DE}. Even though the definition of $R^2$ is different in section \ref{sec:FEM:2D}, the definition of the matrices are the same and are not repeated here.

@@

The equation \eqref{Plate_FEM_M} is the same form as in section \ref{2dFEM_EP} for the two-dimensional elastic body. Therefore the derivation of the eigenvalue problem is identical. Denote the eigenvalue problem for Problem P-1 by Problem P-1E.
\subsubsection{Problem P-1E}
Find a vector function $\bar{u}$ and a number $\lambda$ such that
\begin{eqnarray}
	M\lambda{\bar{u}} & = & K\bar{u}.
\end{eqnarray}

>>>>

\subsubsection{Reference configuration for a rectangular plate}
Let $\left\{e_1,e_2\right\}$ be a right-handed orthonormal basis for $R^2$. Although this basis seems identical to the two-dimensional beam in Section \ref{sssec:2D_Model:RefConf}, it is fact different. It would be more appropriate to use $e_1$ and $e_3$ for this plate model. However the use of $e_1$ and $e_2$ is kept to reiterate that this is in fact a two-dimensional model.

@@

\subsubsection{Cantilever plate model}
Consider a rectangular Reissner-Mindlin plate clamped rigidly to a surface at $\Sigma$ and free hanging on the remaining edges. This plate model is presented in Section \ref{ssec:P_Model:ModelProblems} as Problem P-1.

@@

In Section \ref{ssec:P_Model:ModelProblems} the variational problem for the cantilever Reissner-Mindlin plate is defined by Problem P-1V. For convenience, the relevant results from Section \ref{ssec:P_Model:ModelProblems} are repeated.

@@

\subsection{Galerkin approximation}
To discretise the body $\Omega$, the same shapes as in Section \ref{ssec:2D_Model:Galerkin} are used.

@@

These basis functions are piecewise Hermite bi-cubic basis functions.

@@

\subsection{System of ordinary differential equations}\label{plate_fem_g}
The standard FEM matrices $K_{11}$, $K_{12}$, $K_{21}$, $K_{22}$ and $M_F$ where presented in Section \ref{ssec:2DFEM:DE}. Even though the definition of $R^2$ is different in Section \ref{sec:FEM:2D}, the definition of the matrices are the same and are not repeated here.

@@

The equation \eqref{Plate_FEM_M} is the same form as in Section \ref{2dFEM_EP} for the two-dimensional elastic body. Therefore the derivation of the eigenvalue problem is identical. Denote the eigenvalue problem for Problem P-1 by Problem P-1E.
\subsubsection{Problem P-1E}
Find a vector function $\bar{u}$ and a number $\lambda$ such that
\begin{eqnarray}
	M\lambda{\bar{u}} & = & K\bar{u}.
\end{eqnarray}

### 2024-04-07 files/Chapter6/Introduction.tex
Section capital

\subsubsection{Timoshenko beam}
In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
introduced. The paramater is given here again for convenience,
\begin{eqnarray*}
	\alpha = \frac{A\ell^2}{I}.
\end{eqnarray*}

@@

This special case of plane stress, simplifies the three-dimensional model (see section \ref{sec:2D_Model} In application, this two-dimensional beam can be interpreted as a vertical slice of the three-dimensional beam, where the width of the slice is infinitesimally small. Therefore there is no width parameter $b$ for the two-dimensional beam.

@@

\subsubsection{Reisner-Mindlin plate}
The Reisner-Mindlin plate model is the most different model compared to the rest of the models in this dissertation. The Reisner-Mindlin plate model is derived in section \ref{sec:P_Model}. The model has two parameters, the height $h$ and the width $b$.

>>>>

\subsubsection{Timoshenko beam}
In the derivation of the Timoshenko beam model in Section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
introduced. The paramater is given here again for convenience,
\begin{eqnarray*}
	\alpha = \frac{A\ell^2}{I}.
\end{eqnarray*}

@@

This special case of plane stress, simplifies the three-dimensional model (see Section \ref{sec:2D_Model} In application, this two-dimensional beam can be interpreted as a vertical slice of the three-dimensional beam, where the width of the slice is infinitesimally small. Therefore there is no width parameter $b$ for the two-dimensional beam.

@@

\subsubsection{Reisner-Mindlin plate}
The Reisner-Mindlin plate model is the most different model compared to the rest of the models in this dissertation. The Reisner-Mindlin plate model is derived in Section \ref{sec:P_Model}. The model has two parameters, the height $h$ and the width $b$.

### 2024-04-07 files/Chapter6/Validity_2D.tex
declaration
Section capital

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of a Two-dimensional beam} \label{sec:validity-of-a-2d-beam}

In section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed. In this article, the authors investigated the validity of a cantilever Timoshenko beam by comparing it to a cantilever two-dimensional beam. In this section, the article is extended and the validity of the cantilever two-dimensional model is investigated.

@@

\subsection{The models}
The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in section \ref{ssec:2D_Model:ModelProblem}. From section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D-1.

@@

\subsection{Calculating the eigenvalues}
In section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived. Similar to the two-dimensional case in \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the Finite Element Method is used to calculate the eigenvalues of the three-dimensional beam. The eigenvalue problem for both models have the same form, but different matrices.

\subsubsection{Problem 2D-1E and 3D-1E}
Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	K\bar{u} & = & M\lambda{\bar{u}},
\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in section \ref{ssec:2DFEM:DE} for the Problem 2D-1E and section \ref{3d_fem_g} for Problem 3D-1E.

@@

\subsection{Conclusion}

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of a model for a cantilever two-dimensional beam} \label{sec:validity-of-a-2d-beam}

In Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed. In this article, the authors investigated the validity of a cantilever Timoshenko beam by comparing it to a cantilever two-dimensional beam. In this section, the article is extended and the validity of the cantilever two-dimensional model is investigated.

@@

\subsection{The models}
The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in Section \ref{ssec:2D_Model:ModelProblem}. From Section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D-1.

@@

\subsection{Calculating the eigenvalues}
In Section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived. Similar to the two-dimensional case in \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the Finite Element Method is used to calculate the eigenvalues of the three-dimensional beam. The eigenvalue problem for both models have the same form, but different matrices.

\subsubsection{Problem 2D-1E and 3D-1E}
Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	K\bar{u} & = & M\lambda{\bar{u}},
\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in Section \ref{ssec:2DFEM:DE} for the Problem 2D-1E and Section \ref{3d_fem_g} for Problem 3D-1E.

@@

### 2024-04-07 files/Chapter6/Validity_Plate.tex
Section capital

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of a Reissner-Mindlin plate} \label{sec:validity-of-a-plate}

In the previous section, section \ref{sec:validity-of-a-2d-beam}, it was shown that for certain applications beam models might not be the appropriate choice. The specific application is for models where the body has a larger width than height. A suggestion would be a plate model.

In this section, the validity of a cantilever Reissner-Mindlin plate model is investigated. This model is a two-dimensional model. So similar to the Timoshenko beam in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, it is of value to investigate the validity of the model using a three-dimensional plate model as a reference.

@@

\subsection{The models}
Form section \ref{ssec:P_Model:ModelProblems}, the cantilever Reissner-Mindlin plate model is given, and is referred to as Problem P-1. The three-dimensional model is the same as used in the previous section (section \ref{sec:validity-of-a-2d-beam}), and is referred to as Problem 3D-1 defined in section \ref{ssec:3D_Model:ModelProblems}.

@@

\subsubsection{Problem 3D-1E and P-1E}
Find a vector function $u$ and a number $\lambda$ such that
\begin{eqnarray}
	K{u} & = & M\lambda{u}, 
\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in section \ref{3d_fem_g} for Problem 3D-1E and section \ref{plate_fem_g} for Problem P-1E.

@@

\subsection{Comparing the mode shapes}
Similar to the previous sections (section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and section \ref{sec:validity-of-a-2d-beam}), the mode shapes of the two models are compared, to be able to match up the eigenvalues.

@@

There is less of a dramatic change of the comparison when the width of the plate is changed as with the beam model in section \ref{sec:validity-of-a-2d-beam}. This could be because the Reissner-Mindlin plate model does consider both the width and the height of the plate, while it is only a two-dimensional model. The two-dimensional beam model only considered the height of the beam, and not the width.

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of a model for a cantilever Reissner-Mindlin plate} \label{sec:validity-of-a-plate}

In the previous section, Section \ref{sec:validity-of-a-2d-beam}, it was shown that for certain applications beam models might not be the appropriate choice. The specific application is for models where the body has a larger width than height. A suggestion would be a plate model.

In this section, the validity of a cantilever Reissner-Mindlin plate model is investigated. This model is a two-dimensional model. So similar to the Timoshenko beam in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, it is of value to investigate the validity of the model using a three-dimensional plate model as a reference.

@@

\subsection{The models}
Form Section \ref{ssec:P_Model:ModelProblems}, the cantilever Reissner-Mindlin plate model is given, and is referred to as Problem P-1. The three-dimensional model is the same as used in the previous section (Section \ref{sec:validity-of-a-2d-beam}), and is referred to as Problem 3D-1 defined in Section \ref{ssec:3D_Model:ModelProblems}.

@@

\subsubsection{Problem 3D-1E and P-1E}
Find a vector function $u$ and a number $\lambda$ such that
\begin{eqnarray}
	K{u} & = & M\lambda{u}, 
\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in Section \ref{3d_fem_g} for Problem 3D-1E and Section \ref{plate_fem_g} for Problem P-1E.

@@

\subsection{Comparing the mode shapes}
Similar to the previous sections (Section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and Section \ref{sec:validity-of-a-2d-beam}), the mode shapes of the two models are compared, to be able to match up the eigenvalues.

@@

There is less of a dramatic change of the comparison when the width of the plate is changed as with the beam model in Section \ref{sec:validity-of-a-2d-beam}. This could be because the Reissner-Mindlin plate model does consider both the width and the height of the plate, while it is only a two-dimensional model. The two-dimensional beam model only considered the height of the beam, and not the width.

### 2024-04-07 files/Chapter6/Validity_Timo.tex
Section capital

\subsection{Calculating the eigenvalues and eigenvectors}
In section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided. And in section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.

For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method. In section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived. Specifically, section \ref{2dFEM_EP} derived the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.

\subsubsection{Problem 2D-1E}
Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	K\bar{u} & = & M\lambda{\bar{u}},
\end{eqnarray} where $M$ and $K$ are the standard Finite Element Method matrices defined in section \ref{sec:FEM:2D}.

>>>>

\subsection{Calculating the eigenvalues and eigenvectors}
In Section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided. And in Section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.

For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method. In Section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived. Specifically, Section \ref{2dFEM_EP} derived the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.

\subsubsection{Problem 2D-1E}
Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	K\bar{u} & = & M\lambda{\bar{u}},
\end{eqnarray} where $M$ and $K$ are the standard Finite Element Method matrices defined in Section \ref{sec:FEM:2D}.

### 2024-04-07 files/Chapter7/Beam-Main_Rig_2.tex
Section capital

\subsection{The models}
Consider the cantilever Timoshenko beam model problem Problem T-2 from section \ref{ssec:1D_Model:ModelProblems} and the cantilever two-dimensional beam model problem Problem 2D-1 from section \ref{ssec:2D_Model:ModelProblem}.\\

@@

The parameter $h$ is the height of the two-dimensional beam. Recall the dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ from section \ref{sssec:1D_Model:DimensionlessForm}. For the Timoshenko beam model with a rectangular cross-section, the area moment of inertial is 
\begin{eqnarray*}
	I = \frac{h^3b}{12}.
\end{eqnarray*}

@@

\subsection{Accuracy of the numerical eigenvalues}
For the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} reference an another article \cite{VV06}. In this article \cite{VV06}, a method is described to obtain the eigenvalues and eigenfunctions of a (cantilever) Timoshenko beam. This method also allows for the eigenvalues to be obtained to a desired level of accuracy (using a numerical method such as interval division). In this dissertation, \cite{VV06} is discussed in section \ref{sec:Timo:EigenvalueProblem}.\\

@@

\subsection{The models}
Consider a cantilever two-dimensional beam, referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.\\

>>>>

\subsection{The models}
Consider the cantilever Timoshenko beam model problem Problem T-2 from Section \ref{ssec:1D_Model:ModelProblems} and the cantilever two-dimensional beam model problem Problem 2D-1 from Section \ref{ssec:2D_Model:ModelProblem}.\\

@@

The parameter $h$ is the height of the two-dimensional beam. Recall the dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ from Section \ref{sssec:1D_Model:DimensionlessForm}. For the Timoshenko beam model with a rectangular cross-section, the area moment of inertial is 
\begin{eqnarray*}
	I = \frac{h^3b}{12}.
\end{eqnarray*}

@@

\subsection{Accuracy of the numerical eigenvalues}
For the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} reference an another article \cite{VV06}. In this article \cite{VV06}, a method is described to obtain the eigenvalues and eigenfunctions of a (cantilever) Timoshenko beam. This method also allows for the eigenvalues to be obtained to a desired level of accuracy (using a numerical method such as interval division). In this dissertation, \cite{VV06} is discussed in Section \ref{sec:Timo:EigenvalueProblem}.\\

@@

\subsection{The models}
Consider a cantilever two-dimensional beam, referred to as Problem 2D-1 in Section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in Section \ref{ssec:3D_Model:ModelProblems}.\\

### 2024-04-07 files/Chapter7/Beam.tex
Section capital

\subsection{The models}
Recall the cantilever Timoshenko beam model from section \ref{ssec:1D_Model:ModelProblems}, referred to as Problem T-2 and the cantilever two-dimensional beam model from section \ref{ssec:2D_Model:ModelProblem}, referred to as Problem 2D-1. In \cite{LVV09} it is assumed that the beams have a rectangular cross-section.\\

@@

\subsection{Accuracy of the numerical eigenvalues}
To calculate the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} use the article \cite{VV06}. This article was discussed in section \ref{sec:Timo:EigenvalueProblem} in this dissertation. Using this article, the eigenvalues for the Timoshenko beam model can be numerically calculated to a desired accuracy level.

A different approach is needed for the two-dimensional beam. The Finite Element Method is applied to the eigenvalue problem described in section \ref{sec:FEM:2D}. The following shows the rate of convergence of the first 20 eigenvalues using FEM and bi-cubic basis functions.

@@

The models for the two-dimensional and three-dimensional beams are defined in section \ref{ssec:2D_Model:ModelProblem} and \ref{ssec:3D_Model:ModelProblems} respectively. These models are elastic bodies and not specifically beam models. Therefore it is expected to find eigenvalue and eigenfunction pairs that does not relate to beam type problems. This was already seen with the two-dimensional model in the previous section. These not beam type eigenvalues are calculated in this section, however the focus still remains on beam type problems.\\

\subsection{The models}
Recall a cantilever two-dimensional beam, referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.\\

@@

\subsection{Accuracy of the numerical eigenvalues}
Similar to how the eigenvalues and eigenfunctions of the two-dimensional model calculated in the previous section, the eigenvalues and eigenfunctions can be calculated for the three-dimensional model. The numerical formula to calculate the eigenvalues and eigenfunctions are derived in section \ref{sec:FEM:3D}.\\

>>>>

\subsection{The models}
Recall the cantilever Timoshenko beam model from Section \ref{ssec:1D_Model:ModelProblems}, referred to as Problem T-2 and the cantilever two-dimensional beam model from Section \ref{ssec:2D_Model:ModelProblem}, referred to as Problem 2D-1. In \cite{LVV09} it is assumed that the beams have a rectangular cross-section.\\

@@

\subsection{Accuracy of the numerical eigenvalues}
To calculate the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} use the article \cite{VV06}. This article was discussed in Section \ref{sec:Timo:EigenvalueProblem} in this dissertation. Using this article, the eigenvalues for the Timoshenko beam model can be numerically calculated to a desired accuracy level.

A different approach is needed for the two-dimensional beam. The Finite Element Method is applied to the eigenvalue problem described in Section \ref{sec:FEM:2D}. The following shows the rate of convergence of the first 20 eigenvalues using FEM and bi-cubic basis functions.

@@

The models for the two-dimensional and three-dimensional beams are defined in Section \ref{ssec:2D_Model:ModelProblem} and \ref{ssec:3D_Model:ModelProblems} respectively. These models are elastic bodies and not specifically beam models. Therefore it is expected to find eigenvalue and eigenfunction pairs that does not relate to beam type problems. This was already seen with the two-dimensional model in the previous section. These not beam type eigenvalues are calculated in this section, however the focus still remains on beam type problems.\\

\subsection{The models}
Recall a cantilever two-dimensional beam, referred to as Problem 2D-1 in Section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in Section \ref{ssec:3D_Model:ModelProblems}.\\

@@

\subsection{Accuracy of the numerical eigenvalues}
Similar to how the eigenvalues and eigenfunctions of the two-dimensional model calculated in the previous section, the eigenvalues and eigenfunctions can be calculated for the three-dimensional model. The numerical formula to calculate the eigenvalues and eigenfunctions are derived in Section \ref{sec:FEM:3D}.\\

### 2024-04-07 files/Chapter7/Introduction.tex
Section capital

\subsubsection{Timoshenko beam}
In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is introduced.
\begin{eqnarray*}
	\alpha = \frac{A\ell^2}{I}
\end{eqnarray*}

@@

\subsubsection{Two-dimensional plate}
The two-dimensional plate model is the most different model from the rest of the models. The two-dimensional plate model is a Reissner-Mindlin plate model, and is derived in section \ref{sec:reissnermindlinplate}. The model has two parameters, the height $h$ and the width $b$.

>>>>

\subsubsection{Timoshenko beam}
In the derivation of the Timoshenko beam model in Section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is introduced.
\begin{eqnarray*}
	\alpha = \frac{A\ell^2}{I}
\end{eqnarray*}

@@

\subsubsection{Two-dimensional plate}
The two-dimensional plate model is the most different model from the rest of the models. The two-dimensional plate model is a Reissner-Mindlin plate model, and is derived in Section \ref{sec:reissnermindlinplate}. The model has two parameters, the height $h$ and the width $b$.
